Approximation as Differentiation notes

### 2025-02-25 notes/sec/biproduct.tex
specifying second component of f'(i).

\begin{definition}[Biproduct]
For any objects $A, B$, the \emph{biproduct} of $A$ and $B$ is an object $A \oplus B$ of $C$ together with
morphisms

\begin{center}
\begin{tikzcd}
   A \arrow[r, "i_A", shift left] &
   A \oplus B \arrow[l, "p_A", shift left] \arrow[r, "p_B"', shift right] &
   B \arrow[l, "i_B"', shift right]
\end{tikzcd}
\end{center}

@@

\begin{minipage}[t]{0.45\textwidth}
\begin{center}
\begin{salign*}
   p_A \comp i_A &= \id_A \\
   p_B \comp i_A &= \zero_{A,B}
\end{salign*}
\end{center}
\end{minipage}%
\begin{minipage}[t]{0.45\textwidth}
\begin{center}
\begin{salign*}
   p_B \comp i_B &= \id_B \\
   p_A \comp i_B &= \zero_{B,A}
\end{salign*}
\end{center}
\end{minipage}

@@

\begin{salign*}
i_A \comp p_A + i_B \comp p_B &= \id_{A \oplus B}
\end{salign*}
\end{definition}

If $C$ has biproducts then it has products given by $(A \oplus B, p_A, p_B)$ and coproducts given by $(A
\oplus B, i_A, i_B)$.

>>>>

\begin{definition}[Biproduct]
For any objects $A, B$, the \emph{biproduct} of $A$ and $B$ is an object $A \biprod B$ of $C$ together with
morphisms

\begin{center}
\begin{tikzcd}
   A \arrow[r, "\inj_A", shift left] &
   A \biprod B \arrow[l, "\proj_A", shift left] \arrow[r, "\proj_B"', shift right] &
   B \arrow[l, "\inj_B"', shift right]
\end{tikzcd}
\end{center}

@@

\begin{minipage}[t]{0.45\textwidth}
\begin{center}
\begin{salign*}
   \proj_A \comp \inj_A &= \id_A \\
   \proj_B \comp \inj_A &= \zero_{A,B}
\end{salign*}
\end{center}
\end{minipage}%
\begin{minipage}[t]{0.45\textwidth}
\begin{center}
\begin{salign*}
   \proj_B \comp \inj_B &= \id_B \\
   \proj_A \comp \inj_B &= \zero_{B,A}
\end{salign*}
\end{center}
\end{minipage}

@@

\begin{salign*}
\inj_A \comp \proj_A + \inj_B \comp \proj_B &= \id_{A \proj B}
\end{salign*}
\end{definition}

If $C$ has biproducts then it has products given by $(A \biprod B, \proj_A, \proj_B)$ and coproducts given by $(A
\biprod B, \inj_A, \inj_B)$.
